---
  output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
collapse = TRUE,
comment = "#>",
fig.path = "man/figures/README-",
out.width = "100%"
)
```

```{r, echo=FALSE}
cartridge <- function(x, lifecycle="experimental"){
  repo <- paste0("MomX/", x)
  out <- paste(
    badger::badge_lifecycle(lifecycle),
    badger::badge_cran_release(x, color = "green"),
    badger::badge_travis(repo),
    badger::badge_codecov(repo),
    # badger::badge_cran_download(repo),
    
    # badger::badge_cran_checks(repo),
    "\n\n",
    paste0(
      paste0(" > [", x, " website]("),
      paste0("https://momx.github.io/", x, ")")
    ),
    sep=" "
  )
  cat(out)
}
```

# MomX
*Part of [MomX](https://momx.github.io/MomX/)*

**Note than pretty much none of what follows will be ready before end of April 2020**

MomX is an ecosystem of R packages for everything 2D morphometrics, that
is the statistical description of shape and its (co)variation. 

MomX is
intended to provide a complete, comfortable, powerful, and - last but
not least - open-source workflow for morphometrics.

MomX packages share common principles and work together well. This
architecture is largely inspired by the
[tidyverse](https://tidyverse.org).

### Planned schedule

1. Finish rewriting Momocs, release (April 2020)
2. Port old Momocs stats to Momcalc, release (April 2020)
3. Finish Momit, release (May 2020)
4. Finish MomX, release (May 2020)
5. Finish Momacs and Momoshop, release (June 2020)
6. Submit to [rOpenSci](https://ropensci.org/)

## Packages
### Acquisition

#### `r emo::ji("vulcan_salute")` [Momit](https://github.com/MomX/Momit)

Import from various image and foreing file format and defines a portable format for morphometrics data

```{r, results="asis", echo=FALSE}
cartridge("Momit")
```

#### `r emo::ji("hammer_and_wrench")` [Momacs](https://github.com/MomX/Momacs)

Interactively acquire morphometrics data from images, eg defining landmarks, curves, and other regions of interest.

```{r, results="asis", echo=FALSE}
cartridge("Momacs")
```

#### `r emo::ji("camera")` [Momoshop](https://github.com/MomX/Momoshop)

Post-processes images, eg adjust contrast, pick channels, remove background, etc.

```{r, results="asis", echo=FALSE}
cartridge("Momoshop")
```

### Morphometrics
#### `r emo::ji("dove")` [Momocs](https://github.com/MomX/Momocs)

Manipulating shapes and turning them into coefficients using morphometrics methods.

```{r, results="asis", echo=FALSE}
cartridge("Momocs2")
```


#### `r emo::ji("abacus")` [Momcalc](https://github.com/MomX/Momcalc)

Wraps sensible statistics methods for morphometrics in a consistent grammar

```{r, results="asis", echo=FALSE}
cartridge("Momcalc")
```

#### `r emo::ji("crystal")` [Momecs](https://github.com/MomX/Momecs)
Is the shiny child of Momocs + Momecs

```{r, results="asis", echo=FALSE}
cartridge("Momecs")
```

### Meta
#### `r emo::ji("ring")` [MomX](https://github.com/MomX/MomX)

Install and manage all MomX packages

```{r, results="asis", echo=FALSE}
cartridge("MomX")
```

#### `r emo::ji("books")` [Mombook](https://github.com/MomX/Momocs)

Compiles all package documentation into a practical book for MomX

#### `r emo::ji("do_not_litter")` [MomXiv](https://github.com/MomX/MomXiv)

Share and archive morphometrics data


## General philosophy
* MomX aims to be a complete and user-friendly ecosystem for morphometrics
* Compartiment key processes into well-defined, interoperable packages that go together well.
* Each package should solve a single task, and do it well. Make it work, document, release, improve, repeat.

MomX embraces and owns much to the [tidy manifesto](https://cran.r-project.org/web/packages/tidyverse/vignettes/manifesto.html). MomX kind of theorise the programming side of morphometrics, or at least itself (yes, infinite loop). Tibbles are the answer.

MomX packages share :

* Continous integration with [Travis](travis-ci.org/)
* Continuous testing with [pkg::testthat] and [codecov](https://codecov.io)
* Companion website built by [pkg::pkgdown], at url: `MomX.github.io/packagename`
* Cheatsheets to decorate your bathroom walls


## Installation
__Will come on top when ready__

Once on CRAN, install the last released version of a package, say "MomX" with:

``` r
install.packages("MomX")
```

I will typically only support the very last development versions that you can get from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("MomX/MomX")
```

Then you will need to laod it with :

```{r, eval=FALSE}
library(MomX)
```

You can install and use packages separetely (eg with `install.packages("Momocs")`. `MomX` package will install all MomX packages, and help update them.

## How to help
I'm much than welcoming contributions to MomX ! Good news is that whatever your skills, you can contribute a bit.

You can :

* Signal a bug : fill an issue with __bug__ label :bug:
* Code, improve, develop, discuss, request new features : fill an issue with __discuss__ :wrench:
* Improve examples, and my English : _edit pages_ :uk:

## How to get help
I do not have time either, so before asking for help, please :

* Make sure you have the very last versions of packages : `MomX::MomX_update`
* Start reading the vignettes, they are a good place to start :books:
* Read the reference manual, understand examples :hatching_chick:
* Go to walk for 2 hours in the forest :deciduous_tree: :boar: :four_leaf_clover:, solves 95% of my problems
* Show us what you have tried and make a [reproducible example](https://stackoverflow.com/questions/5963269/how-to-make-a-great-r-reproducible-example) :pill:

Then, if you think something is wrong with :

* is wrong with MomX : fill an issue with __bug__
* is wrong with you, your data, or something local, fill an issue tagged with __help__

Feel free to ring my bell `<bonhomme.vincent@gmail.com>` if :

* You would like to collaborate with me
* You would like to get trained in R and/or MomX
* Any other sensible reason

Happy MomX-ing :kissing_heart: !

