---
  output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
collapse = TRUE,
comment = "#>",
fig.path = "man/figures/README-",
out.width = "100%"
)
```

```{r, echo=FALSE}
library(magrittr)
cartridge <- function(x){
  repo <- paste0("MomX/", x)
  paste(
    badger::badge_travis(repo),
    badger::badge_cran_download(repo),
    badger::badge_cran_release(repo, color = "green"),
    badger::badge_cran_checks(repo),
    sep=" "
  ) %>% cat()
}
```

# MomX
*Part of [MomX](https://momx.github.io/MomX/)*

<!-- badges: start -->
<!-- badges: end -->

MomX is an ecosystem of R packages for everything 2D morphometrics, that
is the statistical description of shape and its (co)variation. It is
intended to provide a complete, comfortable, powerful, and - last but
not least - open-source workflow for morphometrics.

MomX packages share common principles and work together well. This
architecture is largely inspired by the
[tidyverse](https://tidyverse.org).

Planned schedule is :

1. Finish rewriting Momocs, release
2. Port old Momocs stats to Momcalc, release
3. Finish Momit, release
4. Finish MomX, release
5. Finish Momacs and Momoshop, release

## Packages
### Acquisition

#### `r emo::ji("vulcan_salute")` Momit

Import from various image and foreing file format and defines a portable format for morphometrics data

#### `r emo::ji("hammer_and_wrench")` Momacs

Interactively acquire morphometrics data from images, eg defining landmarks, curves, and other regions of interest.

#### `r emo::ji("camera")` Momoshop

Post-processes images, eg adjust contrast, pick channels, remove background, etc.

### Morphometrics
#### `r emo::ji("dove")` [Momocs](https://github.com/MomX/Momocs)


Manipulating shapes and turning them into coefficients using morphometrics methods.

```{r, results="asis", echo=FALSE}
cartridge("Momocs")
```

#### `r emo::ji("abacus")` Momcalc
Wraps sensible statistics methods for morphometrics in a consistent grammar

#### `r emo::ji("crystal")` Momex
Is the shiny child of Momocs + Momecs

### Meta
#### `r emo::ji("ring")` __MomX__ helps install and update MomX packages

#### `r emo::ji("books")` __Mombook__ compiles all package documentation into a practical book for MomX

#### `r emo::ji("do_not_litter")` __MomXiv__ aims at archiving and share morphometrics data

<!--
[![CRAN status](https://www.r-pkg.org/badges/version/Momocs)](https://cran.r-project.org/package=Momocs) 

[![Travis build status](https://travis-ci.org/MomX/Momocs.svg?branch=master)](https://travis-ci.org/MomX/Momocs)


#### :camera: [Momoshop](https://github.com/MomX/Momoshop) : images post-processing 
[![lifecycle](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental) [![CRAN status](https://www.r-pkg.org/badges/version/Momoshop)](https://cran.r-project.org/package=Momoshop)

[![Travis build status](https://travis-ci.org/MomX/Momacs.svg?branch=master)](https://travis-ci.org/MomX/Momacs)

#### :round_pushpin: [Momacs](https://github.com/MomX/Momoshop) : interactive acquisition from images
[![lifecycle](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental) [![CRAN status](https://www.r-pkg.org/badges/version/Momacs)](https://cran.r-project.org/package=Momacs)

[![Travis build status](https://travis-ci.org/MomX/Momoshop.svg?branch=master)](https://travis-ci.org/MomX/Momoshop)


<!--
[![lifecycle](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![Travis build status](https://travis-ci.org/MomX/MomX.svg?branch=master)](https://travis-ci.org/MomX/MomX)
[![CRAN status](https://www.r-pkg.org/badges/version/MomX)](https://cran.r-project.org/package=MomX)
-->

## General philosophy
* MomX aims to be a complete and user-friendly ecosystem for morphometrics
* Compartiment key processes into well-defined, interoperable packages that go together well.
* Each package should solve a single task, and do it well. Make it work, document, release, improve, repeat.

MomX embraces and owns much to the [tidy manifesto](https://cran.r-project.org/web/packages/tidyverse/vignettes/manifesto.html). MomX kind of theorise the programming side of morphometrics, or at least itself (yes, infinite loop). Tibbles are the answer.

MomX packages share :

* Continous integration with [Travis](travis-ci.org/)
* Continuous testing with [pkg::testthat] and [codecov](https://codecov.io)
* Companion website built by [pkg::pkgdown], at url: `MomX.github.io/packagename`
* Cheatsheets to decorate your bathroom walls


## Installation
__Will come on top when ready__

Once on CRAN, install the last released version of a package, say "MomX" with:

``` r
install.packages("MomX")
```

I will typically only support the very last development versions that you can get from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("MomX/MomX")
```

Then you will need to laod it with :

```{r, eval=FALSE}
library(MomX)
```

You can install and use packages separetely (eg with `install.packages("Momocs")`. `MomX` package will install all MomX packages, and help update them.

## How to help
I'm much than welcoming contributions to MomX ! Good news is that whatever your skills, you can contribute a bit.

You can :

* Signal a bug : fill an issue with __bug__ label
* Code, improve, develop, discuss, request new features : fill an issue with __discuss__
* Improve examples, and my English : _edit pages_

## How to get help
I do not have time either, so before asking for help, please :

* Make sure you have the very last versions of packages : `MomX::MomX_update`
* Start reading the vignettes, they are a good place to start
* Read the reference manual, understand examples
* Go to walk for 2 hours in the forest
* Show us what you have tried and make a [reproducible example](https://stackoverflow.com/questions/5963269/how-to-make-a-great-r-reproducible-example)

Then, if you think something is wrong with :

* is wrong with MomX : fill an issue with __bug__
* is wrong with you, your data, or something local, fill an issue tagged with __help__

Feel free to ring my bell `<bonhomme.vincent@gmail.com>` if :

* You would like to collaborate with me
* You would like to get trained in R and/or MomX
* Any other sensible reason

Happy MomX-ing !


<!--


### Advances
This repos will report advances on MomX development.


| Package                                                      | Family        | Description                                  | Lifecycle                                                                                                                         | Passing                                                                                                              | CRAN                                                                                                         |
|--------------------------------------------------------------|---------------|----------------------------------------------|-----------------------------------------------------------------------------------------------------------------------------------|----------------------------------------------------------------------------------------------------------------------|--------------------------------------------------------------------------------------------------------------|
| :camera:[Momoshop](https://github.com/MomX/Momoshop)         | acquisition   | images post-processing                       | [![lifecycle](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental) | [![Travis build status](https://travis-ci.org/MomX/Momacs.svg?branch=master)](https://travis-ci.org/MomX/Momacs)     | [![CRAN status](https://www.r-pkg.org/badges/version/Momoshop)](https://cran.r-project.org/package=Momoshop) |
| :round_pushpin:[Momacs](https://github.com/MomX/Momoshop)    | acquisition   | interactive acquisition from images          | [![lifecycle](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental) | [![Travis build status](https://travis-ci.org/MomX/Momoshop.svg?branch=master)](https://travis-ci.org/MomX/Momoshop) | [![CRAN status](https://www.r-pkg.org/badges/version/Momacs)](https://cran.r-project.org/package=Momacs)     |
| :vulcan_salute:[Momit](https://github.com/MomX/Momit)        | acquisition   | import from images and foreign file format   | [![lifecycle](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental) | [![Travis build status](https://travis-ci.org/MomX/Momit.svg?branch=master)](https://travis-ci.org/MomX/Momit)       | [![CRAN status](https://www.r-pkg.org/badges/version/Momit)](https://cran.r-project.org/package=Momit)       |
| :dove:[Momocs](https://github.com/MomX/Momocs)               | morphometrics | shape manipulation and morphometrics         | [![lifecycle](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental) | [![Travis build status](https://travis-ci.org/MomX/Momocs.svg?branch=master)](https://travis-ci.org/MomX/Momocs)     | [![CRAN status](https://www.r-pkg.org/badges/version/Momocs)](https://cran.r-project.org/package=Momocs)     |
| :eagle:[Momstats](https://github.com/MomX/Momstats)          | morphometrics | statistical analyses of morphometric data    | [![lifecycle](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental) | [![Travis build status](https://travis-ci.org/MomX/Momstats.svg?branch=master)](https://travis-ci.org/MomX/Momstats) | [![CRAN status](https://www.r-pkg.org/badges/version/Momstats)](https://cran.r-project.org/package=Momstats) |
| :hatching_chick:[Momclick](https://github.com/MomX/Momclick) | morphometrics | the two previous, made interactive           | [![lifecycle](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental) | [![Travis build status](https://travis-ci.org/MomX/Momclick.svg?branch=master)](https://travis-ci.org/MomX/Momclick) | [![CRAN status](https://www.r-pkg.org/badges/version/Momclick)](https://cran.r-project.org/package=Momclick) |
| :ring:[MomX](https://github.com/MomX/MomX)                   | meta          | to install, reinstall, load some or them all | [![lifecycle](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental) | [![Travis build status](https://travis-ci.org/MomX/MomX.svg?branch=master)](https://travis-ci.org/MomX/MomX)         | [![CRAN status](https://www.r-pkg.org/badges/version/MomX)](https://cran.r-project.org/package=MomX)         |
| :blue_book:[Mombook](https://github.com/MomX/Mombook)        | meta          | a book collating all vignettes               | [![lifecycle](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental) | _no CI_                                                                                                              | _not for CRAN_                                                                                               |
| :package:[Momdata](https://github.com/MomX/Momdata)          | meta          | a data package                               | [![lifecycle](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental) | [![Travis build status](https://travis-ci.org/MomX/Momdata.svg?branch=master)](https://travis-ci.org/MomX/Momdata)   | _not for CRAN_                                                                                               |
|                                                              |               |                                              |                                                                                                                                   |                                                                                                                      |                                                                                                              |

-->

<!--
### Packages

#### :dove: [Momocs](https://github.com/MomX/Momocs): shape manipulation and morphometrics
[![lifecycle](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental) [![CRAN status](https://www.r-pkg.org/badges/version/Momocs)](https://cran.r-project.org/package=Momocs) 

[![Travis build status](https://travis-ci.org/MomX/Momocs.svg?branch=master)](https://travis-ci.org/MomX/Momocs)

#### :camera: [Momoshop](https://github.com/MomX/Momoshop) : images post-processing 
[![lifecycle](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental) [![CRAN status](https://www.r-pkg.org/badges/version/Momoshop)](https://cran.r-project.org/package=Momoshop)

[![Travis build status](https://travis-ci.org/MomX/Momacs.svg?branch=master)](https://travis-ci.org/MomX/Momacs)

#### :round_pushpin: [Momacs](https://github.com/MomX/Momoshop) : interactive acquisition from images
[![lifecycle](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental) [![CRAN status](https://www.r-pkg.org/badges/version/Momacs)](https://cran.r-project.org/package=Momacs)

[![Travis build status](https://travis-ci.org/MomX/Momoshop.svg?branch=master)](https://travis-ci.org/MomX/Momoshop)




### General philosophy
* MomX aims to be a complete and user-friendly ecosystem for morphometrics
* Compartiment key processes into well-defined, interoperable packages that go together well.
* Each package should solve a single task, and do it well. Make it work, document, release, improve, repeat.

MomX embraces and owns much to the [tidy manifesto](https://cran.r-project.org/web/packages/tidyverse/vignettes/manifesto.html). MomX kind of theorise the programming side of morphometrics, or at least itself (yes, infinite loop). Tibbles are the answer.

MomX packages share :
* Companion website built by [pkg::pkgdown]
* Continous integration with [Travis](travis-ci.org/)
* Continuous testing with [pkg::testthat] and [codecov](https://codecov.io)

###


### How to help
I'm much than welcoming contributions to MomX ! Good news is that whatever your skills, you can contribute a bit.

You can :

* Signal a bug 
* Discuss or request a feature
* Code, improve, develop new features
* Improve examples, and my English
* Share datasets

### How to get helped
* Vignettes are a good place to start
* Read the reference manual, understand examples
* Go to walk for 2 hours in the forest

Then, if you think something :

* is wrong with Momocs, fill an issue with __bug__
* is wrong with you, your data, or something local, fill an issue tagged with __help__
* would be fantastic, fill an issue with __request__

...



| Package | Lifecycle                                                                                                                         | Travis                                                                                                              | CRAN                                                                                                         | Website                                               |
| ------- | --------------------------------------------------------------------------------------------------------------------------------- | ------------------------------------------------------------------------------------------------------------------- | ------------------------------------------------------------------------------------------------------------ | ----------------------------------------------------- |
| MomX    | [![lifecycle](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental) | [![Travis build status](https://travis-ci.org/MomX/MomX.svg?branch=master)](https://travis-ci.org/MomX/MomX)        | [![CRAN status](https://www.r-pkg.org/badges/version/MomX)](https://cran.r-project.org/package=MomX)         | [MomX.github.io/MomX](http://momx.github.io/MomX)     |
| Momacs  | [![lifecycle](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental) | [![Travis build status](https://travis-ci.org/MomX/Momacs.svg?branch=master)](https://travis-ci.org/MomX/Momacs)    | [![CRAN status](https://www.r-pkg.org/badges/version/Momacs)](https://cran.r-project.org/package=Momacs)     | <https://github.com/MomX/Momacs>                      |
| Momit   | [![lifecycle](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental) | [![Travis build status](https://travis-ci.org/MomX/Momit.svg?branch=master)](https://travis-ci.org/MomX/Momit)      | [![CRAN status](https://www.r-pkg.org/badges/version/Momit)](https://cran.r-project.org/package=Momit)       | [MomX.github.io/Momit](http://momx.github.io/Momit)   |
| Momocs  | [![lifecycle](https://img.shields.io/badge/lifecycle-maturing-blue.svg)](https://www.tidyverse.org/lifecycle/#maturing)           | [![Travis-CI Build Status](https://travis-ci.org/MomX/Momocs.svg?branch=master)](https://travis-ci.org/MomX/Momocs) | [![CRAN Status Badge](http://www.r-pkg.org/badges/version/Momocs)](http://cran.r-project.org/package=Momocs) | [MomX.github.io/Momocs](http://momx.github.io/Momocs) |
| Momecs  | [![lifecycle](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental) | [![Travis build status](https://travis-ci.org/MomX/Momecs.svg?branch=master)](https://travis-ci.org/MomX/Momecs)    | [![CRAN status](https://www.r-pkg.org/badges/version/Momecs)](https://cran.r-project.org/package=Momecs)     | [MomX.github.io/Momecs](http://momx.github.io/Momecs) |

Other protypic MomX packages
follows:

| Package  | Lifecycle                                                                                                                         | Travis                                                                                                             | CRAN                                                                                                       | Website                                                 |
| -------- | --------------------------------------------------------------------------------------------------------------------------------- | ------------------------------------------------------------------------------------------------------------------ | ---------------------------------------------------------------------------------------------------------- | ------------------------------------------------------- |
| Momfarm  | [![lifecycle](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental) | [![Travis build status](https://travis-ci.org/MomX/Momfarm.svg?branch=master)](https://travis-ci.org/MomX/Momfarm) | [![CRAN status](https://www.r-pkg.org/badges/version/Momfarm)](https://cran.r-project.org/package=Momfarm) | [MomX.github.io/Momfarm](http://momx.github.io/Momfarm) |
| Momoshop | [![lifecycle](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental) | soon                                                                                                               | soon                                                                                                       | soon                                                    |

