---
output:
  github_document:
    html_preview: false
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
## MomX  
_Part of [MomX](https://momx.github.io/MomX/)_

<!--
[![lifecycle](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![Travis build status](https://travis-ci.org/MomX/MomX.svg?branch=master)](https://travis-ci.org/MomX/MomX)
[![CRAN status](https://www.r-pkg.org/badges/version/MomX)](https://cran.r-project.org/package=MomX)
-->

#### News
* I plan a first working version of all packages in July/August 2018.
* Drop me a line if you want you me to send updates (1 email per month at most) or simply get in touch for any other reason: `bonhomme.vincent@gmail.com`

----

MomX is an ecosystem of R packages for everything 2D morphometrics, that is the statistical description of shape and its (co)variation. It is intended to provide a complete, comfortable, powerful, and - last but not least - open-source workflow for morphometrics in R.

MomX packages share common principles and work together well. This architecture is largely inspired by the [tidyverse](https://tidyverse.org). 

Core MomX currently includes:

* __[MomX](https://momx.github.io/MomX/)__: make it easy to install/load/update all MomX packages
* __[Momacs](https://github.com/MomX/Momacs)__: acquisition of morphometrics data
* __[Momit](http://momx.github.io/Momit/)__: morphometrics data conversion and exchange
* __[Momocs](http://momx.github.io/Momocs/)__: the mothership of MomX, complete 2D morphometrics toolbox from shapes and collections of shapes
* __[Momecs](http://momx.github.io/Momecs/)__: multivariate analyses for multivariate data, notably morphometrics

You can follow their development/status below:

Package     |  Lifecycle    |  Travis    |  CRAN      | Website
------------|---------------|------------|------------| ---------------
MomX        | [![lifecycle](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental) | [![Travis build status](https://travis-ci.org/MomX/MomX.svg?branch=master)](https://travis-ci.org/MomX/MomX) | [![CRAN status](https://www.r-pkg.org/badges/version/MomX)](https://cran.r-project.org/package=MomX) | [MomX.github.io/MomX](http://momx.github.io/MomX)
Momacs      | [![lifecycle](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental) | [![Travis build status](https://travis-ci.org/MomX/Momacs.svg?branch=master)](https://travis-ci.org/MomX/Momacs) | [![CRAN status](https://www.r-pkg.org/badges/version/Momacs)](https://cran.r-project.org/package=Momacs) | [https://github.com/MomX/Momacs](https://github.com/MomX/Momacs)
Momit      | [![lifecycle](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental) | [![Travis build status](https://travis-ci.org/MomX/Momit.svg?branch=master)](https://travis-ci.org/MomX/Momit) | [![CRAN status](https://www.r-pkg.org/badges/version/Momit)](https://cran.r-project.org/package=Momit) | [MomX.github.io/Momit](http://momx.github.io/Momit)
Momocs      | [![lifecycle](https://img.shields.io/badge/lifecycle-maturing-blue.svg)](https://www.tidyverse.org/lifecycle/#maturing) | [![Travis-CI Build Status](https://travis-ci.org/MomX/Momocs.svg?branch=master)](https://travis-ci.org/MomX/Momocs) | [![CRAN Status Badge](http://www.r-pkg.org/badges/version/Momocs)](http://cran.r-project.org/package=Momocs) | [MomX.github.io/Momocs](http://momx.github.io/Momocs)
Momecs      | [![lifecycle](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental) | [![Travis build status](https://travis-ci.org/MomX/Momecs.svg?branch=master)](https://travis-ci.org/MomX/Momecs) | [![CRAN status](https://www.r-pkg.org/badges/version/Momecs)](https://cran.r-project.org/package=Momecs) | [MomX.github.io/Momecs](http://momx.github.io/Momecs)

Other protypic MomX packages follows:

Package     |  Lifecycle    |  Travis    |  CRAN      | Website
------------|---------------|------------|------------| ---------------
Momfarm     | [![lifecycle](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)  | [![Travis build status](https://travis-ci.org/MomX/Momfarm.svg?branch=master)](https://travis-ci.org/MomX/Momfarm) | [![CRAN status](https://www.r-pkg.org/badges/version/Momfarm)](https://cran.r-project.org/package=Momfarm) | [MomX.github.io/Momfarm](http://momx.github.io/Momfarm)
Momoshop    |  [![lifecycle](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)  | soon | soon | soon 

### Installation
The (future) released version will be installable from [CRAN](https://CRAN.R-project.org/package=MomX ) with:

```{r cran-installation, eval = FALSE}
install.packages("MomX")
```

But, so far, and for all MomX packages, I strongly recommend (and typically only support) using the development version that can be installed from GitHub with:
```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("MomX/MomX")
```

Then, all MomX packages (only Momocs so far) will be loadable with a single call to:

```{r attach, eval=TRUE}
library(MomX)
```

MomX packages can be attached, detached, updated from CRAN, updated from [GitHub](http://github.com/MomX) with:
```{r update, eval=FALSE}
MomX_attach()        # equivalent to: library(MomX)
MomX_detach()
MomX_update_cran()
MomX_update_github()
```
